¥section{REED command line flags summary}¥label{flagsSummary}
The following summary was generated automatically by using ¥texttt{reed‾-summarise}, running REED version 2.3. Compiled 10:02:24, Mar 13 2026.
¥vskip 5mm¥begin{description}¥raggedright
¥item[¥tt -¥#]‾¥¥ show comments in the REED file, useful if comments are used as reminders.

¥item[¥tt -basename <path/file.ext>]‾¥¥ set pathname for generated files (replacing ¥texttt{.ext} with ¥texttt{.gv}, ¥texttt{.html}, ¥texttt{.pdf}, etc).

¥item[¥tt -c]‾¥¥ show weakly connected components.

¥item[¥tt -allcolors]‾¥¥ list all colors that are available for highlighting.

¥item[¥tt -colors]‾¥¥ list all colors used.

¥item[¥tt -colors+]‾¥¥ lists all colors like ¥texttt{-colors} but also gives the meanings of all colors used.

¥item[¥tt -F]‾¥¥ highlight flags in graph drawing --- unfortunately due to a GraphViz bug, this breaks up any groups.

¥item[¥tt -f]‾¥¥ show textual descriptions of flag colors in REED drawing.

¥item[¥tt -flags]‾¥¥ show all flag definitions.

¥item[¥tt -g]‾¥¥ generate a GraphViz ¥texttt{.gv} file --- default option if nothing else chosen --- See ¥texttt{https://graphviz.org} for details.

¥item[¥tt -go]‾¥¥ as ¥texttt{-g} but also open the ¥texttt{.gv} file.

¥item[¥tt -h]‾¥¥ generate an interactive ¥texttt{.html} REED file.

¥item[¥tt -ho]‾¥¥ as ¥texttt{-h} but also open the ¥texttt{.html} file.

¥item[¥tt -ids]‾¥¥ show full names and IDs in graph.

¥item[¥tt -insert <text>]‾¥¥ insert this text to process before next file.

¥item[¥tt -json]‾¥¥ generate a JSON ¥texttt{.js} file with all information from the GraphViz diagram.

¥item[¥tt -keywords]‾¥¥ list all keywords used.

¥item[¥tt -l]‾¥¥ generate a Latex REED file --- also generates some useful Latex definition files.

¥item[¥tt -m]‾¥¥ generate a Mathematica ¥texttt{.nb} file representing the REED graph as a series of expressions.

¥item[¥tt -n]‾¥¥ show node IDs in graph drawing.

¥item[¥tt -o]‾¥¥ open generated files automatically.

¥item[¥tt -pdf]‾¥¥ generate a ¥texttt{.pdf} file representing the REED graph.

¥item[¥tt -pick <color>]‾¥¥ restrict generated files to just this color.

¥item[¥tt -pick <keyword>]‾¥¥ restrict generated files to notes with this keyword. Keyword can be abbreviated: use ¥texttt{...} so ¥texttt{xyz...} matches keywords or phrases starting ¥texttt{xyz}.

¥item[¥tt -pick+ <color>]‾¥¥ same as ¥texttt{-pick} but also explains this color meaning.

¥item[¥tt -raw]‾¥¥ start in raw mode (skipping text until a start tag) --- only use ¥texttt{-raw} with ¥texttt{-tags} flag.

¥item[¥tt -rules]‾¥¥ summarise HTML-Latex rules.

¥item[¥tt -s]‾¥¥ list nodes and their full names, sorted by node ID.

¥item[¥tt -ss]‾¥¥ list nodes and their full names, sorted by full names.

¥item[¥tt -sss]‾¥¥ list nodes and their full names, sorted by both node ID and full names.

¥item[¥tt -sep]‾¥¥ draw a separator line before processing any files (useful with ¥texttt{-watch}).

¥item[¥tt -sig]‾¥¥ show REED file signatures.

¥item[¥tt -summarise]‾¥¥ put Latex overview of REED syntax and command line flags to standard output.

¥item[¥tt -svg]‾¥¥ generate a ¥texttt{.svg} file --- representing the REED graph.

¥item[¥tt -syntax]‾¥¥ summarise REED syntax.

¥item[¥tt -t]‾¥¥ transpose node numbering --- swap row and column node numbers.

¥item[¥tt -tags <start> <end>]‾¥¥ only process REED information written between these tags --- you can change tags between files --- and also set tags within a REED file by: ¥texttt{tags <start> <end>}.

¥item[¥tt -transit]‾¥¥ list transit nodes and nodes with no influence.

¥item[¥tt -v]‾¥¥ verbose mode.

¥item[¥tt -version]‾¥¥ state the version number of the REED command.

¥item[¥tt -w]‾¥¥ what versions are used in these files? --- helpful to know if using the ¥texttt{v=} flag.

¥item[¥tt -watch]‾¥¥ run REED when any used file changes (nice with ¥texttt{-o} flag).

¥item[¥tt -x]‾¥¥ generate an ¥texttt{.xml} file --- representing all REED data for import into other applications.

¥item[¥tt --]‾¥¥ treat all further parameters as filenames --- if you want to have no restrictions on filenames as they otherwise cannot be flags.

¥end{description}
¥section{REED syntax summary}¥label{syntaxSummary}
The following summary was generated automatically by using ¥texttt{reed‾-summarise}, running REED version 2.3. Compiled 10:02:24, Mar 13 2026.
¥vskip 5mm
{¥tt¥noindent¥hbox{}‾‾‾‾{¥rm ¥#‾Hash‾¥#‾indicates‾comment‾to‾end‾of‾line}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾Hash‾¥#‾is‾also‾used‾for‾comments‾in‾this‾syntax‾summary}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾syntax‾notation...}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾blanks‾can‾be‾put‾between‾all‾syntactic‾items‾and‾used‾freely‾for‾layout‾}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾x‾::=‾y‾{¥rm ¥#‾define‾non-terminal‾¥texttt{x}‾to‾be‾¥texttt{y}}¥¥
¥hbox{}‾‾‾‾x‾¥texttt{|}‾y‾‾‾{¥rm ¥#‾¥texttt{x}‾or‾¥texttt{y}}¥¥
¥hbox{}‾‾‾‾¥{‾x‾¥}‾‾‾{¥rm ¥#‾grouping‾in‾syntax‾definitions}¥¥
¥hbox{}‾‾‾‾x+‾‾‾‾‾‾{¥rm ¥#‾at‾least‾one‾¥texttt{x}.‾Short‾for:‾¥texttt{x}‾¥texttt{|}‾¥texttt{x}¥texttt{x}‾¥texttt{|}‾¥texttt{x}¥texttt{x}¥texttt{x}‾¥texttt{|}‾...}¥¥
¥hbox{}‾‾‾‾x++‾‾‾‾‾{¥rm ¥#‾at‾least‾one‾¥texttt{x}‾separated‾by‾spaces.‾Short‾for:‾¥texttt{x}‾¥texttt{|}‾¥texttt{x}‾¥texttt{x}‾¥texttt{|}‾¥texttt{x}‾¥texttt{x}‾¥texttt{x}‾¥texttt{|}...‾}¥¥
¥hbox{}‾‾‾‾[‾x‾]‾‾‾{¥rm ¥#‾optional‾¥texttt{x}}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾REED‾syntax...}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾id‾::=‾¥{‾letter‾¥texttt{|}‾digit‾¥texttt{|}‾underline‾¥texttt{|}‾dot‾¥}+‾¥texttt{|}‾Cstring‾¥texttt{|}‾Herestring¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾Cstring‾::=‾"C‾string,‾¥textbackslash¥@n‾for‾newline,‾¥textbackslash¥@¥textbackslash¥@‾for‾backslash‾etc"‾¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾Herestring‾::=‾<<<‾arbitrary-terminator¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾characters‾(no‾escapes‾needed)‾over‾any‾number‾of‾lines¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾ends‾with‾same‾arbitrary-terminator‾text¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾at‾start‾of‾line¥¥
¥hbox{}‾‾‾‾arbitrary-terminator¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾properties‾::=‾¥{‾id1‾:‾id2‾¥}++¥¥
¥hbox to 3em{}{¥rm Used‾in‾¥texttt{note‾id}‾to‾define‾property‾¥texttt{id1}‾of‾¥texttt{id}‾as‾¥texttt{id2}}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾narrative‾strings‾used‾in‾notes‾are‾translated‾to‾HTML‾and/or‾Latex}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾use‾¥texttt{-rules}‾to‾summarise‾the‾automatic‾HTML/Latex‾translations}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾narrative‾strings‾can‾include:}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾<html>‾...‾‾‾‾‾‾‾‾{¥rm ¥#‾following‾text‾is‾copied‾to‾HTML,‾but‾skipped‾in‾Latex}¥¥
¥hbox{}‾‾‾‾<latex>‾...‾‾‾‾‾‾‾{¥rm ¥#‾following‾text‾is‾copied‾to‾Latex,‾but‾skipped‾in‾HTML}¥¥
¥hbox{}‾‾‾‾<both>‾...‾‾‾‾‾‾‾‾{¥rm ¥#‾following‾text‾is‾mixed‾basic‾HTML‾and‾Latex}¥¥
¥hbox{}‾‾‾‾<input>‾filename‾‾{¥rm ¥#‾insert‾the‾text‾contents‾of‾file‾¥texttt{filename}‾into‾the‾string}¥¥
¥hbox{}‾‾‾‾[[[id]]]‾‾‾‾‾‾‾‾‾‾{¥rm ¥#‾replace‾with‾¥texttt{id}‾name‾and‾make‾a‾cross-reference‾link}¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾{¥rm ¥#‾(¥texttt{[[[id]]]}‾makes‾links‾in‾both‾HTML‾and‾Latex)}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾reserved‾words‾can‾be‾used‾as‾ids‾if‾written‾out‾as‾strings}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾otherwise,‾an‾id‾¥texttt{xyz}‾and‾a‾string‾¥texttt{"xyz"}‾are‾equivalent}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾so‾¥texttt{check}‾(a‾command)‾is‾reserved,‾but‾¥texttt{"check"}‾can‾be‾used‾arbitrarily}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾string‾notations‾also‾allow‾more‾characters,‾like‾newlines,‾to‾be‾used}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾the‾following‾are‾definitions‾of‾non-terminals:}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾arrow‾::=‾influences:‾¥texttt{|}‾->‾¥texttt{|}‾<-‾¥¥
¥hbox{}‾‾‾‾color‾::=‾aqua‾¥texttt{|}‾black‾¥texttt{|}‾blue‾¥texttt{|}‾fuchsia‾¥texttt{|}‾gray‾¥texttt{|}‾green¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾¥texttt{|}‾lime‾¥texttt{|}‾maroon‾¥texttt{|}‾navy‾¥texttt{|}‾olive‾¥texttt{|}‾orange‾¥texttt{|}‾purple¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾¥texttt{|}‾red‾¥texttt{|}‾silver‾¥texttt{|}‾teal‾¥texttt{|}‾white‾¥texttt{|}‾yellow¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾note‾that‾color‾names‾cannot‾be‾used‾as‾ids}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#‾NB‾¥texttt{reed‾-allcolors}‾lists‾all‾supported‾colors}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾id-or-star‾::=‾id‾¥texttt{|}‾*¥¥
¥hbox{}‾‾‾‾node-list‾::=‾id‾¥texttt{|}‾(‾id++‾)¥¥
¥hbox{}‾‾‾‾node-or-arrow‾::=‾id‾¥texttt{|}‾id‾¥{‾arrow‾id‾¥}+¥¥
¥hbox{}‾‾‾‾node-or-arrow-list‾::=‾node-or-arrow‾¥texttt{|}‾(‾node-or-arrow++‾)¥¥
¥hbox{}‾‾‾‾document-property‾::=‾title‾¥texttt{|}‾author‾¥texttt{|}‾abstract‾¥texttt{|}‾date‾¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾¥texttt{|}‾introduction‾¥texttt{|}‾conclusion‾¥texttt{|}‾latexdefinitions¥¥
¥hbox{}‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾‾¥texttt{|}‾htmldefinitions¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾the‾following‾are‾REED‾statements}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾all‾terminals‾below‾are‾reserved‾words}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾reserved‾words‾can‾use‾lower‾and‾upper‾case‾letters‾freely}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾check‾id1‾=>‾id2¥¥
¥hbox to 3em{}{¥rm Check‾there‾is‾a‾path‾from‾¥texttt{id1}‾to‾¥texttt{id2}}¥¥
¥hbox{}‾‾‾‾cycle‾node-list¥¥
¥hbox to 3em{}{¥rm Confirms‾that‾these‾nodes‾are‾intended‾to‾be‾on‾a‾cycle,‾and‾do‾not‾report‾them}¥¥
¥hbox{}‾‾‾‾direction‾¥{‾LR‾¥texttt{|}‾RL‾¥texttt{|}‾TB‾¥texttt{|}‾BT‾¥}¥¥
¥hbox to 3em{}{¥rm Primary‾direction‾of‾graph‾is‾left-right,‾right-left,‾top-bottom,‾or‾bottom-top}¥¥
¥hbox{}‾‾‾‾definitions.html‾id¥¥
¥hbox to 3em{}{¥rm Insert‾¥texttt{id}‾at‾start‾of‾¥texttt{body}‾in‾HTML‾file;‾multiple‾¥texttt{definitions}‾concatenate}¥¥
¥hbox{}‾‾‾‾definitions.latex‾id¥¥
¥hbox to 3em{}{¥rm Insert‾¥texttt{id}‾at‾start‾of‾Latex‾file}¥¥
¥hbox to 3em{}{¥rm multiple‾¥texttt{definitions}‾concatenate‾}¥¥
¥hbox{}‾‾‾‾definitions.latexend‾id¥¥
¥hbox to 3em{}{¥rm Insert‾¥texttt{id}‾at‾end‾of‾Latex‾file‾(e.g.,‾for‾references)}¥¥
¥hbox to 3em{}{¥rm multiple‾¥texttt{definitions}‾concatenate‾}¥¥
¥hbox{}‾‾‾‾document-property‾id¥¥
¥hbox to 3em{}{¥rm Specify‾document‾properties.‾Details‾append‾when‾given‾multiple‾times}¥¥
¥hbox{}‾‾‾‾group‾node-or-arrow-list‾is‾id¥¥
¥hbox to 3em{}{¥rm The‾nodes‾are‾grouped,‾and‾the‾group‾is‾named‾¥texttt{id}}¥¥
¥hbox{}‾‾‾‾highlight‾color‾[‾cascade‾]‾is‾id¥¥
¥hbox to 3em{}{¥rm Define‾meaning‾of‾color‾as‾¥texttt{id}}¥¥
¥hbox to 3em{}{¥rm If‾cascade‾is‾specified,‾apply‾to‾all‾nodes‾the‾¥texttt{color}‾influences}¥¥
¥hbox{}‾‾‾‾highlight‾id‾[‾cascade‾]‾is‾color¥¥
¥hbox to 3em{}{¥rm Highlight‾node‾¥texttt{id}‾with‾¥texttt{color}}¥¥
¥hbox to 3em{}{¥rm Optional‾¥texttt{cascade}‾colors‾all‾nodes‾¥texttt{id}‾influences}¥¥
¥hbox{}‾‾‾‾layout‾[‾TOC‾]‾(‾¥{‾id‾(‾id++‾)‾¥}++‾)¥¥
¥hbox to 3em{}{¥rm Draw‾a‾graph‾with‾a‾structured‾layout,‾with‾optional‾TOC‾(Theory‾of‾Change)‾styling}¥¥
¥hbox{}‾‾‾‾node-or-arrow‾[‾is‾id‾]¥¥
¥hbox to 3em{}{¥rm Create‾nodes‾or‾arrows,‾with‾optional‾display‾name‾¥texttt{id}}¥¥
¥hbox{}‾‾‾‾norefs¥¥
¥hbox to 3em{}{¥rm Nodes‾without‾reference‾numbers‾will‾not‾be‾reported‾as‾errors}¥¥
¥hbox{}‾‾‾‾note‾node-or-arrow-list‾[‾properties‾]‾[‾is‾id1‾[;]‾]‾id3¥¥
¥hbox to 3em{}{¥rm Provide‾narrative‾note‾¥texttt{id3}‾for‾the‾nodes‾or‾arrows,‾optionally‾naming‾them‾¥texttt{id1}}¥¥
¥hbox{}‾‾‾‾numbering‾(‾¥{‾(‾id-or-star++‾)‾¥}++‾)¥¥
¥hbox to 3em{}{¥rm Make‾node‾references‾row.column‾numbers‾following‾the‾grid‾layout}¥¥
¥hbox{}‾‾‾‾ref‾id1‾is‾id2¥¥
¥hbox to 3em{}{¥rm Set‾the‾reference‾of‾node‾¥texttt{id1}‾to‾be‾¥texttt{id2}}¥¥
¥hbox{}‾‾‾‾style‾node-or-arrow-list‾is‾id¥¥
¥hbox to 3em{}{¥rm Set‾style‾of‾nodes‾or‾arrows‾to‾a‾Dot‾specification,}¥¥
¥hbox to 3em{}{¥rm which‾can‾contain‾further‾REED‾style‾names‾(see‾¥texttt{style.new})}¥¥
¥hbox{}‾‾‾‾style.cycle‾id¥¥
¥hbox to 3em{}{¥rm Define‾style‾to‾highlight‾cycles}¥¥
¥hbox{}‾‾‾‾style.default‾id¥¥
¥hbox to 3em{}{¥rm Define‾default‾style‾for‾nodes‾and‾edges}¥¥
¥hbox{}‾‾‾‾style.new‾id1‾is‾id2¥¥
¥hbox to 3em{}{¥rm Define‾¥texttt{id1}‾as‾a‾style,‾using‾Dot‾syntax‾for‾¥texttt{id2}}¥¥
¥hbox to 3em{}{¥rm ¥texttt{id2}‾can‾contain‾further‾REED‾style‾names‾(but‾not‾recursively)}¥¥
¥hbox{}‾‾‾‾tags‾id1‾id2¥¥
¥hbox to 3em{}{¥rm Only‾process‾REED‾code‾between‾¥texttt{id1}‾(begin)‾and‾¥texttt{id2}‾(end)}¥¥
¥hbox{}‾‾‾‾version‾id¥¥
¥hbox to 3em{}{¥rm Subsequent‾REED‾code‾is‾version‾¥texttt{id}‾(see‾flag‾¥texttt{v=value})}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾;¥¥
¥hbox to 3em{}{¥rm semicolons‾are‾empty‾statements}¥¥
¥hbox to 3em{}{¥rm Semicolons‾can‾be‾placed‾freely‾between‾statements,‾and‾in‾¥texttt{note}‾statements‾to‾aid‾legibility}¥¥
¥hbox{}¥¥
¥hbox{}¥¥
¥hbox to 3em{}{¥rm The‾order‾of‾commands‾generally‾does‾not‾matter}¥¥
¥hbox to 3em{}{¥rm Except:‾}¥¥
¥hbox to 3em{}{¥rm ¥texttt{author},‾¥texttt{definitions.html},‾¥texttt{definitions.latex},‾¥texttt{definitions.latexend}‾which‾concatenate}¥¥
¥hbox to 3em{}{¥rm and‾¥texttt{tag}‾and‾¥texttt{version},‾which‾are‾executed‾in‾the‾order‾stated}¥¥
¥hbox{}¥¥
¥hbox{}‾‾‾‾{¥rm ¥#¥#¥#‾Technical‾note‾on‾style‾names‾and‾spaces:}¥¥
¥hbox{}‾‾‾‾Style‾names‾defined‾by‾<style.new‾id>‾can‾be‾used‾anywhere‾in‾styles,¥¥
¥hbox{}‾‾‾‾which‾means‾<id>‾must‾be‾surrounded‾by‾spaces‾to‾be‾recognised¥¥
¥hbox{}‾‾‾‾e.g.,‾<xidy>‾has‾to‾be‾written‾<x‾id‾y>‾for‾<id>‾to‾be‾recognised¥¥
¥hbox{}‾‾‾‾or‾of‾courses‾can‾be‾written‾<x;id;y>‾etc.¥¥
¥hbox{}‾‾‾‾Any‾spaces‾around‾using‾<id>‾will‾be‾stripped‾off,¥¥
¥hbox{}‾‾‾‾so‾if‾you‾do‾need‾spaces‾around‾a‾named‾style¥¥
¥hbox{}‾‾‾‾those‾spaces‾have‾to‾be‾put‾in‾the‾definition‾of‾<id>.¥¥
¥hbox{}}
